---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r, echo=TRUE}
activity <- read.csv(unz('activity.zip', 'activity.csv'), sep = ',')
activity$date <- as.Date(activity$date, format = '%Y-%m-%d')
```


## What is mean total number of steps taken per day?

```{r, echo=TRUE}
library(dplyr)
activity_bydate <- activity %>%
        group_by(date) %>%
        summarise_all(sum)
library(ggplot2)
g <- ggplot(data = activity_bydate, aes(x = date, y = steps))
g + geom_bar(stat = 'identity')

```

### Mean total number of steps taken per day
```{r}
mean(activity_bydate$steps, na.rm = TRUE)
```
### Median total number of steps taken per day
```{r}
median(activity_bydate$steps, na.rm = TRUE)
```
## What is the average daily activity pattern?

```{r, echo=TRUE}
library(dplyr)
activity_byinterval <- activity %>%
        group_by(interval) %>%
        summarise_all(mean, na.rm = TRUE)
library(ggplot2)
g <- ggplot(data = activity_byinterval, aes(x = interval, y = steps))
g + geom_line()

```

### Maximum number of steps 
```{r}
activity_byinterval[which.max(activity_byinterval$steps),1]
```


## Imputing missing values
### Total number of missing values
```{r}
sum(is.na(activity))
```
### Filling in all of the missing values in the dataset by the median for that 5-minute interval and creating new dataset
```{r}
activity_filled_NA <- activity %>%
        group_by(interval)%>%
        mutate(steps = ifelse(is.na(steps), median(steps, na.rm = TRUE), steps))
```
### Histogram of the total number of steps taken each day after imputing missing values

```{r, echo=TRUE}
library(dplyr)
activity_bydate_imput <- activity_filled_NA %>%
        group_by(date) %>%
        summarise_all(sum)
library(ggplot2)
g <- ggplot(data = activity_bydate_imput, aes(x = date, y = steps))
g + geom_bar(stat = 'identity')

```

### Mean total number of steps taken per day after imputing
```{r}
mean(activity_bydate_imput$steps)
```
### Median total number of steps taken per day after imputing
```{r}
median(activity_bydate_imput$steps)
```
 As we can see mean and median numbers after imputing are lover then before. 
## Are there differences in activity patterns between weekdays and weekends?
